REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case

### 2017-12-21 main.tex
Update on Overleaf.

\section{Methods}
\label{sec:methods}
In 
%mm brief, 
     summary, 
we produce high-resolution galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background. We 
%mm 
    assume collisional ionization equilibrium for all other elements in order to
use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure. In addition, we follow the optically thin non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner dissociation of molecular hydrogen. We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernovae progenitors. We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star
%mm
   as it forms
with the associated local gas abundances for each species. These methods are discussed in full detail below.

@@

% figure here of mass loading and mass outflow rates
\begin{figure*}
\centering
\includegraphics[width=0.33\linewidth]{total_mass_outflow}
\includegraphics[width=0.33\linewidth]{total_mass_loading}
\includegraphics[width=0.33\linewidth]{metal_mass_loading}
\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
\label{fig:mass_outflow}
\end{figure*}

@@

\subsection{Chemical Evolution} 
\label{sec:chemical evolution}
\textbf{Commented out all previous discussion of species abundance retention differences and stellar abundances to save for a future paper. Instead, here give a panel plot showing the column densities of the metals at various times?}

>>>>

\section{Methods}
\label{sec:methods}
In 
%mm brief, 
     summary, 
we produce high-resolution galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background. We 
%mm 
    assume collisional ionization equilibrium for all other elements in order to
use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure. In addition, we follow the optically thin non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner dissociation of molecular hydrogen. We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernovae progenitors. We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star
%mm
   as it forms
with the associated local gas abundances for each species. In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked. This field is used to inform the heating/cooling physics and determines the metallicity of each star. These methods are discussed in full detail below.

@@

% figure here of mass loading and mass outflow rates
\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{total_mass_outflow}
\includegraphics[width=0.45\linewidth]{total_mass_loading}
%\includegraphics[width=0.33\linewidth]{metal_mass_loading}
\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
\label{fig:mass_outflow}
\end{figure*}

@@

\subsection{Metal Evolution} 
\label{sec:chemical evolution}
\textbf{Commented out all previous discussion of species abundance retention differences and stellar abundances to save for a future paper. Instead, here give a panel plot showing the column densities of the metals at various times?}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
\includegraphics[width=0.9\linewidth]{metal_fraction_evolution}
\caption{Top: Metal mass loading factor at four radii over time (see text for how this is defined). Bottom: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time. In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
\label{fig:metal_evolution}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=0.23\linewidth]{metal_mass_loading} 
\includegraphics[width=0.23\linewidth]{metal_fraction_evolution}
\includegraphics[width=0.23\linewidth]{metal_mass_loading} 
\includegraphics[width=0.23\linewidth]{metal_fraction_evolution}
\caption{Full-box projections of the entire computational domain showing the total column density in each of 4 different metal species at the end of the simulation time. For a more reasonable comparison across metal fields with significant differences total column density, the maximum of the color bar scales are each set to the peak column density for that field, and the minimum to a fixed fraction of this maximum.}
\label{fig:metal_column_panels}
\end{figure*}
